{\bf {\Large Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico}}

### 2016-09-28 ident_manu.tex
table/figure revisions, about to look at identbox for all state variables

\begin{singlespace}
\title{{\bf {\Large Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$, Lisa L. Lowe$^2$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
	\\\\{\textit {\normalsize $^2$Lockheed Martin IS \& GS - Civil, supporting the USEPA}}
	\\{\textit {\normalsize Resarch Triangle Park, NC 27709}}
	\\{\textit {\normalsize Phone: 919-541-3985,}}
	\\{\textit {\normalsize Email: \href{mailto:lowe.lisa@epa.gov}{lowe.lisa@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Fri Sep 23 17:24:42 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

%latex.default(totab[, -c(1, 2)], file = "", rowlabel = "Parameter",     caption = cap_val, caption.loc = "top", size = "scriptsize",     label = "tab:heurist1", rowname = parms, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), colheads = colnms, rgroupTexCmd = NULL)%

@@

{Optics}&&&&&&&&&\tabularnewline

@@

{Organic Matter}&&&&&&&&&\tabularnewline

@@

{Phytoplankton}&&&&&&&&&\tabularnewline

@@

{Zooplankton}&&&&&&&&&\tabularnewline

@@

% second heuristic, all states
%latex.default(totab[, -c(1, 2)], file = "", rowlabel = "Selections by state variable",     caption = cap_val, caption.loc = "top", size = "scriptsize",     label = "tab:heurist2", rowname = sels, rgroup = unique(stts),     n.rgroup = as.numeric(table(stts)), colheads = colnms, rgroupTexCmd = NULL)%
\begin{table}[!tbp]
{\scriptsize
\caption{Parameter identifiability (as $\gamma$, \cref{gameq}) for relevant state variables.  Selections followed the second heuristic where parameters were selected independent of category from most to least sensitive until $\gamma > 15$.  Rank describes the relative parameter sensitivity in each category for each state variable (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton). See \cref{fig:heurist_stts} for a graphical illustration.\label{tab:heurist2}} 
\begin{center}
\begin{tabular}{llll}
\hline\hline
\multicolumn{1}{l}{Selections by state variable}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Rank}&\multicolumn{1}{c}{$\gamma$}\tabularnewline
\hline
{Ammonium}&&&\tabularnewline
~~1&\scriptsize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
~~2&\scriptsize{\textit{nitmax}}&$1$\textsuperscript{OM}&$1.16$\tabularnewline
~~3&\scriptsize{\textit{Zumax}}&$1$\textsuperscript{Z}&$2.9$\tabularnewline
\hline
{Chlorophyll}&&&\tabularnewline
~~1&\scriptsize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
~~2&\scriptsize{\textit{Zumax}}&$1$\textsuperscript{Z}&$1.18$\tabularnewline
\hline
{Dissolved Oxygen}&&&\tabularnewline
~~1&\scriptsize{\textit{umax}}&$1$\textsuperscript{P}&$1$\tabularnewline
~~2&\scriptsize{\textit{ZKa}}&$1$\textsuperscript{Z}&$2.17$\tabularnewline
~~3&\scriptsize{\textit{mA}}&$2$\textsuperscript{P}&$2.31$\tabularnewline
~~4&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsuperscript{T}&$2.37$\tabularnewline
~~5&\scriptsize{\textit{ZQn}}&$2$\textsuperscript{Z}&$4.69$\tabularnewline
~~6&\scriptsize{\textit{alpha}}&$3$\textsuperscript{P}&$4.91$\tabularnewline
~~7&\scriptsize{\textit{Zm}}&$3$\textsuperscript{Z}&$6.73$\tabularnewline
~~8&\scriptsize{\textit{Zumax}}&$4$\textsuperscript{Z}&$6.81$\tabularnewline
\hline
{Irradiance}&&&\tabularnewline
~~1&\scriptsize{\textit{ZKa}}&$1$\textsuperscript{Z}&$1$\tabularnewline
~~2&\scriptsize{\textit{umax}}&$1$\textsuperscript{P}&$4.41$\tabularnewline
~~3&\scriptsize{\textit{ZQn}}&$2$\textsuperscript{Z}&$7.54$\tabularnewline
~~4&\scriptsize{\textit{mA}}&$2$\textsuperscript{P}&$8.17$\tabularnewline
~~5&\scriptsize{\textit{KGcdom}}&$1$\textsuperscript{OM}&$9.44$\tabularnewline
~~6&\scriptsize{\textit{alpha}}&$3$\textsuperscript{P}&$9.66$\tabularnewline
~~7&\scriptsize{\textit{Zumax}}&$3$\textsuperscript{Z}&$10.79$\tabularnewline
\hline
{Nitrate}&&&\tabularnewline
~~1&\scriptsize{\textit{umax}}&$1$\textsuperscript{P}&$1$\tabularnewline
\hline
{OM1}&&&\tabularnewline
~~1&\scriptsize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
~~2&\scriptsize{\textit{Zumax}}&$1$\textsuperscript{Z}&$1.15$\tabularnewline
~~3&\scriptsize{\textit{KG1}}&$1$\textsuperscript{OM}&$3.87$\tabularnewline
\hline
{OM2}&&&\tabularnewline
~~1&\scriptsize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
~~2&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsuperscript{T}&$1.05$\tabularnewline
~~3&\scriptsize{\textit{umax}}&$2$\textsuperscript{P}&$2.46$\tabularnewline
~~4&\scriptsize{\textit{Zumax}}&$1$\textsuperscript{Z}&$2.91$\tabularnewline
\hline
{Phosphate}&&&\tabularnewline
~~1&\scriptsize{\textit{ZKa}}&$1$\textsuperscript{Z}&$1$\tabularnewline
~~2&\scriptsize{\textit{umax}}&$1$\textsuperscript{P}&$11.45$\tabularnewline
~~3&\scriptsize{\textit{vmaxP}}&$2$\textsuperscript{P}&$11.48$\tabularnewline
~~4&\scriptsize{\textit{ZQn}}&$2$\textsuperscript{Z}&$13.74$\tabularnewline
\hline
\end{tabular}\end{center}}

@@

%latex.default(totab[, -c(1, 2)], file = "", rowlabel = "Selections by state variable",     caption = cap_val, caption.loc = "top", size = "scriptsize",     label = "tab:heurist3", rowname = sels, rgroup = unique(stts),     n.rgroup = as.numeric(table(stts)), colheads = colnms, rgroupTexCmd = NULL)%

@@

{Ammonium}&&&\tabularnewline

@@

{Chlorophyll}&&&\tabularnewline

@@

{Dissolved Oxygen}&&&\tabularnewline

@@

{Irradiance}&&&\tabularnewline

@@

{Nitrate}&&&\tabularnewline

@@

{OM1}&&&\tabularnewline

@@

{OM2}&&&\tabularnewline

@@

{Phosphate}&&&\tabularnewline

@@

%latex.default(totab_all[, -c(1, 2)], file = "", rowlabel = "State variables by parameter category",     caption = cap_val, caption.loc = "top", size = "scriptsize",     label = "tab:inistrchg", rowname = stts, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), colheads = colnms, rgroupTexCmd = NULL)%

@@

\caption{Changes in mean sensitivity of state variables by parameter categories to different initial conditions and changes in structural components of the model.  Changes show the difference in average sensitivity from results using the default model setup. Sensitivities are based on average $L1$ (see \cref{l1}) values of the state variables to changes in parameters in each parameter category. Increases in average sensitivity are in bold. Medians and ranges of sensitivity values for the different conditions are shown in \cref{fig:inistrsumm}.\label{tab:inistrchg}} 

@@

\begin{tabular}{lllll}

@@

\multicolumn{1}{l}{State variables by parameter category}&\multicolumn{1}{c}{Default sensitivity}&\multicolumn{1}{c}{Initial: April}&\multicolumn{1}{c}{Initial: September}&\multicolumn{1}{c}{Structure: complex}\tabularnewline

@@

{Optics}&&&&\tabularnewline
~~Ammonium&$0.01$&$\bm{0.01}$&$\bm{0.01}$&$\bm{0.01}$\tabularnewline
~~Chlorophyll&$0.01$&$\bm{0.01}$&$\bm{0.01}$&$\bm{0.01}$\tabularnewline
~~Dissolved Oxygen&$2.81\times 10^{-4}$&$\bm{2.11\times 10^{-4}}$&$\bm{1.46\times 10^{-4}}$&$\bm{1.93\times 10^{-4}}$\tabularnewline
~~Irradiance&$0.01$&$-0$&$-0$&$-0$\tabularnewline
~~Nitrate&$0.01$&$\bm{0.01}$&$\bm{0.01}$&$\bm{0.01}$\tabularnewline
~~OM1&$0.01$&$\bm{0.01}$&$\bm{0.01}$&$\bm{0.01}$\tabularnewline
~~OM2&$0.02$&$\bm{0.01}$&$\bm{0.01}$&$\bm{0.01}$\tabularnewline
~~Phosphate&$0$&$\bm{0}$&$\bm{0}$&$\bm{0}$\tabularnewline

@@

{Organic Matter}&&&&\tabularnewline
~~Ammonium&$0.31$&$-0.08$&$-0.04$&$\bm{2.22\times 10^{-4}}$\tabularnewline
~~Chlorophyll&$0.02$&$-0.12$&$-0.14$&$\bm{0.01}$\tabularnewline
~~Dissolved Oxygen&$0$&$\bm{6.75\times 10^{-4}}$&$-2.32\times 10^{-4}$&$\bm{0}$\tabularnewline
~~Irradiance&$0.01$&$-0.01$&$-0.01$&$\bm{2.99\times 10^{-4}}$\tabularnewline
~~Nitrate&$0.12$&$-0.06$&$-0.09$&$\bm{0.1}$\tabularnewline
~~OM1&$0.13$&$-0.15$&$-0.12$&$-0.04$\tabularnewline
~~OM2&$0.14$&$-0.07$&$-0.17$&$-0.05$\tabularnewline
~~Phosphate&$0.03$&$-0.04$&$-0.06$&$\bm{0.02}$\tabularnewline

@@

{Phytoplankton}&&&&\tabularnewline
~~Ammonium&$0.8$&$\bm{0.02}$&$-0.3$&$-65.98$\tabularnewline
~~Chlorophyll&$1.14$&$-1.23$&$-4.38$&$-104.24$\tabularnewline
~~Dissolved Oxygen&$0.01$&$\bm{4.58\times 10^{-4}}$&$-0$&$-3.44\times 10^{-4}$\tabularnewline
~~Irradiance&$0.02$&$\bm{0}$&$-0$&$-0.01$\tabularnewline
~~Nitrate&$0.74$&$\bm{0.43}$&$\bm{0.45}$&$\bm{0.64}$\tabularnewline
~~OM1&$0.76$&$-0.17$&$-0.46$&$-55.11$\tabularnewline
~~OM2&$1.28$&$-0.34$&$-1.15$&$-128.93$\tabularnewline
~~Phosphate&$0.17$&$-0.03$&$-0.05$&$\bm{0.14}$\tabularnewline

@@

{Temperature}&&&&\tabularnewline
~~Ammonium&$0.79$&$\bm{0.69}$&$\bm{0.69}$&$-272.31$\tabularnewline
~~Chlorophyll&$0.6$&$\bm{0.47}$&$\bm{0.45}$&$-114.51$\tabularnewline
~~Dissolved Oxygen&$0.02$&$\bm{0.02}$&$\bm{0.02}$&$\bm{0.01}$\tabularnewline
~~Irradiance&$0.03$&$\bm{0.02}$&$\bm{0.02}$&$-0.01$\tabularnewline
~~Nitrate&$0.3$&$\bm{0.15}$&$\bm{0.16}$&$\bm{0.19}$\tabularnewline
~~OM1&$0.86$&$\bm{0.68}$&$\bm{0.69}$&$-215.17$\tabularnewline
~~OM2&$1.48$&$\bm{1.21}$&$\bm{1.2}$&$-900.26$\tabularnewline
~~Phosphate&$0.16$&$\bm{0.11}$&$\bm{0.09}$&$\bm{0.11}$\tabularnewline

@@

{Zooplankton}&&&&\tabularnewline
~~Ammonium&$0.47$&$\bm{0.45}$&$\bm{0.44}$&$\bm{0.16}$\tabularnewline
~~Chlorophyll&$0.39$&$\bm{0.26}$&$\bm{0.23}$&$\bm{0.2}$\tabularnewline
~~Dissolved Oxygen&$0.01$&$\bm{0.01}$&$\bm{0.01}$&$\bm{0.01}$\tabularnewline
~~Irradiance&$0.03$&$\bm{0.02}$&$\bm{0.02}$&$\bm{0.01}$\tabularnewline
~~Nitrate&$1.06$&$\bm{1.02}$&$\bm{1.02}$&$\bm{0.98}$\tabularnewline
~~OM1&$0.37$&$\bm{0.27}$&$\bm{0.28}$&$\bm{0.18}$\tabularnewline
~~OM2&$0.39$&$\bm{0.3}$&$\bm{0.28}$&$\bm{0.18}$\tabularnewline
~~Phosphate&$0.31$&$\bm{0.19}$&$\bm{0.17}$&$\bm{0.27}$\tabularnewline

>>>>

\begin{singlespace}
\title{{\bf {\Large Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$, Lisa L. Lowe$^2$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
	\\\\{\textit {\normalsize $^2$Lockheed Martin IS \& GS - Civil, supporting the USEPA}}
	\\{\textit {\normalsize Resarch Triangle Park, NC 27709}}
	\\{\textit {\normalsize Phone: 919-541-3985,}}
	\\{\textit {\normalsize Email: \href{mailto:lowe.lisa@epa.gov}{lowe.lisa@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Tue Sep 27 17:40:51 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

%latex.default(totab[, -c(1, 2)], file = "", rowlabel = "Parameter",     caption = cap_val, caption.loc = "top", size = "scriptsize",     label = "tab:heurist1", rowname = parms, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), colheads = colnms)%

@@

{\bfseries Optics}&&&&&&&&&\tabularnewline

@@

{\bfseries Organic Matter}&&&&&&&&&\tabularnewline

@@

{\bfseries Phytoplankton}&&&&&&&&&\tabularnewline

@@

{\bfseries Zooplankton}&&&&&&&&&\tabularnewline

@@

% second heuristic, all states
%latex.default(totab[, -c(1, 2)], file = "", rowlabel = "Selections by state variable",     caption = cap_val, caption.loc = "top", size = "scriptsize",     label = "tab:heurist2", rowname = sels, rgroup = unique(stts),     n.rgroup = as.numeric(table(stts)), colheads = colnms)%
\begin{table}[!tbp]
{\scriptsize
\caption{Parameter identifiability (as $\gamma$, \cref{gameq}) for relevant state variables.  Selections followed the second heuristic where parameters were selected independent of category from most to least sensitive until $\gamma > 15$.  Rank describes the relative parameter sensitivity in each category for each state variable (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton). See \cref{fig:heurist_stts} for a graphical illustration.\label{tab:heurist2}} 
\begin{center}
\begin{tabular}{llll}
\hline\hline
\multicolumn{1}{l}{Selections by state variable}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Rank}&\multicolumn{1}{c}{$\gamma$}\tabularnewline
\hline
{\bfseries Ammonium}&&&\tabularnewline
~~1&\scriptsize{\textit{mA}}&$1$\textsubscript{P}&$1$\tabularnewline
~~2&\scriptsize{\textit{nitmax}}&$1$\textsubscript{OM}&$1.16$\tabularnewline
~~3&\scriptsize{\textit{Zumax}}&$1$\textsubscript{Z}&$2.9$\tabularnewline
\hline
{\bfseries Chlorophyll}&&&\tabularnewline
~~1&\scriptsize{\textit{mA}}&$1$\textsubscript{P}&$1$\tabularnewline
~~2&\scriptsize{\textit{Zumax}}&$1$\textsubscript{Z}&$1.18$\tabularnewline
\hline
{\bfseries Dissolved Oxygen}&&&\tabularnewline
~~1&\scriptsize{\textit{umax}}&$1$\textsubscript{P}&$1$\tabularnewline
~~2&\scriptsize{\textit{ZKa}}&$1$\textsubscript{Z}&$2.17$\tabularnewline
~~3&\scriptsize{\textit{mA}}&$2$\textsubscript{P}&$2.31$\tabularnewline
~~4&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsubscript{T}&$2.37$\tabularnewline
~~5&\scriptsize{\textit{ZQn}}&$2$\textsubscript{Z}&$4.69$\tabularnewline
~~6&\scriptsize{\textit{alpha}}&$3$\textsubscript{P}&$4.91$\tabularnewline
~~7&\scriptsize{\textit{Zm}}&$3$\textsubscript{Z}&$6.73$\tabularnewline
~~8&\scriptsize{\textit{Zumax}}&$4$\textsubscript{Z}&$6.81$\tabularnewline
\hline
{\bfseries Irradiance}&&&\tabularnewline
~~1&\scriptsize{\textit{ZKa}}&$1$\textsubscript{Z}&$1$\tabularnewline
~~2&\scriptsize{\textit{umax}}&$1$\textsubscript{P}&$4.41$\tabularnewline
~~3&\scriptsize{\textit{ZQn}}&$2$\textsubscript{Z}&$7.54$\tabularnewline
~~4&\scriptsize{\textit{mA}}&$2$\textsubscript{P}&$8.17$\tabularnewline
~~5&\scriptsize{\textit{KGcdom}}&$1$\textsubscript{OM}&$9.44$\tabularnewline
~~6&\scriptsize{\textit{alpha}}&$3$\textsubscript{P}&$9.66$\tabularnewline
~~7&\scriptsize{\textit{Zumax}}&$3$\textsubscript{Z}&$10.79$\tabularnewline
\hline
{\bfseries Nitrate}&&&\tabularnewline
~~1&\scriptsize{\textit{umax}}&$1$\textsubscript{P}&$1$\tabularnewline
\hline
{\bfseries OM1}&&&\tabularnewline
~~1&\scriptsize{\textit{mA}}&$1$\textsubscript{P}&$1$\tabularnewline
~~2&\scriptsize{\textit{Zumax}}&$1$\textsubscript{Z}&$1.15$\tabularnewline
~~3&\scriptsize{\textit{KG1}}&$1$\textsubscript{OM}&$3.87$\tabularnewline
\hline
{\bfseries OM2}&&&\tabularnewline
~~1&\scriptsize{\textit{mA}}&$1$\textsubscript{P}&$1$\tabularnewline
~~2&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsubscript{T}&$1.05$\tabularnewline
~~3&\scriptsize{\textit{umax}}&$2$\textsubscript{P}&$2.46$\tabularnewline
~~4&\scriptsize{\textit{Zumax}}&$1$\textsubscript{Z}&$2.91$\tabularnewline
\hline
{\bfseries Phosphate}&&&\tabularnewline
~~1&\scriptsize{\textit{ZKa}}&$1$\textsubscript{Z}&$1$\tabularnewline
~~2&\scriptsize{\textit{umax}}&$1$\textsubscript{P}&$11.45$\tabularnewline
~~3&\scriptsize{\textit{vmaxP}}&$2$\textsubscript{P}&$11.48$\tabularnewline
~~4&\scriptsize{\textit{ZQn}}&$2$\textsubscript{Z}&$13.74$\tabularnewline
\hline
\end{tabular}\end{center}}

@@

%latex.default(totab[, -c(1, 2)], file = "", rowlabel = "Selections by state variable",     caption = cap_val, caption.loc = "top", size = "scriptsize",     label = "tab:heurist3", rowname = sels, rgroup = unique(stts),     n.rgroup = as.numeric(table(stts)), colheads = colnms)%

@@

{\bfseries Ammonium}&&&\tabularnewline

@@

{\bfseries Chlorophyll}&&&\tabularnewline

@@

{\bfseries Dissolved Oxygen}&&&\tabularnewline

@@

{\bfseries Irradiance}&&&\tabularnewline

@@

{\bfseries Nitrate}&&&\tabularnewline

@@

{\bfseries OM1}&&&\tabularnewline

@@

{\bfseries OM2}&&&\tabularnewline

@@

{\bfseries Phosphate}&&&\tabularnewline

@@

%latex.default(totab_all[, -c(1, 2)], file = "", rowlabel = "State variables by parameter category",     caption = cap_val, caption.loc = "top", size = "scriptsize",     label = "tab:inistrchg", rowname = stts, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), colheads = colnms, cgroup = c("",         "Change"), n.cgroup = c(1, 3))%

@@

\caption{Changes in mean sensitivity of state variables by parameter categories to different initial conditions and structural components of the model.  Changes show the difference in average sensitivity from results using the default model setup. Sensitivities are based on average $L1$ (see \cref{l1}) values of the state variables to changes in parameters in each parameter category. Increases in average sensitivity are in bold. Medians and ranges of sensitivity values for the different conditions are shown in \cref{fig:inistrsumm}.\label{tab:inistrchg}} 

@@

\begin{tabular}{llclll}

@@

\multicolumn{1}{l}{\bfseries State variables by parameter category}&\multicolumn{1}{c}{\bfseries }&\multicolumn{1}{c}{\bfseries }&\multicolumn{3}{c}{\bfseries Change}\tabularnewline
\cline{4-6}
\multicolumn{1}{l}{}&\multicolumn{1}{c}{Default sensitivity}&\multicolumn{1}{c}{}&\multicolumn{1}{c}{Initial: April}&\multicolumn{1}{c}{Initial: September}&\multicolumn{1}{c}{Structure: complex}\tabularnewline

@@

{\bfseries Optics}&&&&&\tabularnewline
~~Ammonium&$0.01$&&$\bm{0.01}$&$\bm{0.01}$&$\bm{0.01}$\tabularnewline
~~Chlorophyll&$0.01$&&$\bm{0.01}$&$\bm{0.01}$&$\bm{0.01}$\tabularnewline
~~Dissolved Oxygen&$2.81\times 10^{-4}$&&$\bm{2.11\times 10^{-4}}$&$\bm{1.46\times 10^{-4}}$&$\bm{1.93\times 10^{-4}}$\tabularnewline
~~Irradiance&$0.01$&&$-0$&$-0$&$-0$\tabularnewline
~~Nitrate&$0.01$&&$\bm{0.01}$&$\bm{0.01}$&$\bm{0.01}$\tabularnewline
~~OM1&$0.01$&&$\bm{0.01}$&$\bm{0.01}$&$\bm{0.01}$\tabularnewline
~~OM2&$0.02$&&$\bm{0.01}$&$\bm{0.01}$&$\bm{0.01}$\tabularnewline
~~Phosphate&$0$&&$\bm{0}$&$\bm{0}$&$\bm{0}$\tabularnewline

@@

{\bfseries Organic Matter}&&&&&\tabularnewline
~~Ammonium&$0.31$&&$-0.08$&$-0.04$&$\bm{2.22\times 10^{-4}}$\tabularnewline
~~Chlorophyll&$0.02$&&$-0.12$&$-0.14$&$\bm{0.01}$\tabularnewline
~~Dissolved Oxygen&$0$&&$\bm{6.75\times 10^{-4}}$&$-2.32\times 10^{-4}$&$\bm{0}$\tabularnewline
~~Irradiance&$0.01$&&$-0.01$&$-0.01$&$\bm{2.99\times 10^{-4}}$\tabularnewline
~~Nitrate&$0.12$&&$-0.06$&$-0.09$&$\bm{0.1}$\tabularnewline
~~OM1&$0.13$&&$-0.15$&$-0.12$&$-0.04$\tabularnewline
~~OM2&$0.14$&&$-0.07$&$-0.17$&$-0.05$\tabularnewline
~~Phosphate&$0.03$&&$-0.04$&$-0.06$&$\bm{0.02}$\tabularnewline

@@

{\bfseries Phytoplankton}&&&&&\tabularnewline
~~Ammonium&$0.8$&&$\bm{0.02}$&$-0.3$&$-65.98$\tabularnewline
~~Chlorophyll&$1.14$&&$-1.23$&$-4.38$&$-104.24$\tabularnewline
~~Dissolved Oxygen&$0.01$&&$\bm{4.58\times 10^{-4}}$&$-0$&$-3.44\times 10^{-4}$\tabularnewline
~~Irradiance&$0.02$&&$\bm{0}$&$-0$&$-0.01$\tabularnewline
~~Nitrate&$0.74$&&$\bm{0.43}$&$\bm{0.45}$&$\bm{0.64}$\tabularnewline
~~OM1&$0.76$&&$-0.17$&$-0.46$&$-55.11$\tabularnewline
~~OM2&$1.28$&&$-0.34$&$-1.15$&$-128.93$\tabularnewline
~~Phosphate&$0.17$&&$-0.03$&$-0.05$&$\bm{0.14}$\tabularnewline

@@

{\bfseries Temperature}&&&&&\tabularnewline
~~Ammonium&$0.79$&&$\bm{0.69}$&$\bm{0.69}$&$-272.31$\tabularnewline
~~Chlorophyll&$0.6$&&$\bm{0.47}$&$\bm{0.45}$&$-114.51$\tabularnewline
~~Dissolved Oxygen&$0.02$&&$\bm{0.02}$&$\bm{0.02}$&$\bm{0.01}$\tabularnewline
~~Irradiance&$0.03$&&$\bm{0.02}$&$\bm{0.02}$&$-0.01$\tabularnewline
~~Nitrate&$0.3$&&$\bm{0.15}$&$\bm{0.16}$&$\bm{0.19}$\tabularnewline
~~OM1&$0.86$&&$\bm{0.68}$&$\bm{0.69}$&$-215.17$\tabularnewline
~~OM2&$1.48$&&$\bm{1.21}$&$\bm{1.2}$&$-900.26$\tabularnewline
~~Phosphate&$0.16$&&$\bm{0.11}$&$\bm{0.09}$&$\bm{0.11}$\tabularnewline

@@

{\bfseries Zooplankton}&&&&&\tabularnewline
~~Ammonium&$0.47$&&$\bm{0.45}$&$\bm{0.44}$&$\bm{0.16}$\tabularnewline
~~Chlorophyll&$0.39$&&$\bm{0.26}$&$\bm{0.23}$&$\bm{0.2}$\tabularnewline
~~Dissolved Oxygen&$0.01$&&$\bm{0.01}$&$\bm{0.01}$&$\bm{0.01}$\tabularnewline
~~Irradiance&$0.03$&&$\bm{0.02}$&$\bm{0.02}$&$\bm{0.01}$\tabularnewline
~~Nitrate&$1.06$&&$\bm{1.02}$&$\bm{1.02}$&$\bm{0.98}$\tabularnewline
~~OM1&$0.37$&&$\bm{0.27}$&$\bm{0.28}$&$\bm{0.18}$\tabularnewline
~~OM2&$0.39$&&$\bm{0.3}$&$\bm{0.28}$&$\bm{0.18}$\tabularnewline
~~Phosphate&$0.31$&&$\bm{0.19}$&$\bm{0.17}$&$\bm{0.27}$\tabularnewline
